---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(maps)
Temp_StateData <- read.csv("~/Desktop/stat451/Temp_StateData.csv")
```


```{r}
help(package = "maps")
?map_data

my_worldmap <- map_data("world")

ggplot(data = my_worldmap, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(fill = "white", color = "black")
```

suppose we want to map just the country Germany

```{r}
germany <- filter(my_worldmap, region == "Germany")
ggplot(data = germany, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(fill = "white", color = "black")
```

suppose now we are interested in multiple countries for example lets select france and germany

```{r}
germany_france <- filter(my_worldmap, region == "Germany" | region == "France")
ggplot(data = germany_france, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(fill = "white", color = "black")+coord_map()
```

##choropleth maps
we will begin by creating a map of usa

```{r}
my_usa <- map_data("state")

ggplot(data = my_usa, mapping = aes(x = long, y = lat, group = group))+geom_polygon(fill = "white", color = "black")

states <- unique(my_usa$region)
```

Join the data using the region as the column for merging.

```{r}
map_data_combined <- left_join(my_usa, Temp_StateData, by = "region")
```

## to make a choropleth map with deafult colors

```{r}
ggplot(data = map_data_combined, mapping = aes(x = long, y = lat, group = group, fill = AvgTemp))+
  geom_polygon(color = "black")+
  theme_grey()
```

##changing the color pallete

```{r}
ggplot(data = map_data_combined, mapping = aes(x = long, y = lat, group = group, fill = AvgTemp))+
  geom_polygon(color = "blue")+
  scale_fill_viridis_c(option = "B")
```

```{r}
world <- map_data("world")
india <- filter(world,region == "India")
```

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")
```

```{r}
head(maps::world.cities)
my_cities <- maps::world.cities
```

```{r}
india_cities <- filter(my_cities, country.etc == "India")
```

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
geom_polygon(color = "black", fill = "white")+
geom_point(data = india_cities, aes(x = long, y = lat,group = NULL),color = "blue")
```

```{r}
india_big_cities <- filter(my_cities, country.etc == "India" & pop > 1000000)
```


#reacreating map of india with only big cities ploted on it
```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")+
  geom_point(data = india_big_cities, aes(x = long, y = lat,group = NULL),color = "blue")
```
#vary the size of the points by population

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")+
  geom_point(data = india_big_cities, aes(x = long, y = lat,group = NULL, size = pop),color = "blue")
```

#To vary the color of the dots we will create a fake categorical data column
```{r}
india_big_cities$qual <- sample(LETTERS[1:5], nrow(india_big_cities), replace = TRUE)
```

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")+
  geom_point(data = india_big_cities, aes(x = long, y = lat,group = NULL, size = pop, color = qual))
```

```{r}
india_big_cities$Population <- india_big_cities$pop
india_big_cities$Qualitative <- india_big_cities$qual
```

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")+
  geom_point(data = india_big_cities, aes(x = long, y = lat,group = NULL, size = pop),color = Qualitative)
```

```{r}
ggplot(data = india, mapping = aes(x = long, y = lat, group = group))+
  geom_polygon(color = "black", fill = "white")+
  geom_point(data = india_big_cities, aes(x = long, y = lat, group = NULL, size = Population, color = Qualitative))
```